Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-03 paper/paper.tex
more polishing

To sum up, \tname{} uses the messages that manifest an attack in the
first step to create a potentially over-specified seed rule. Then, it
uses benign traffic in the second step to create a set of plausible
rules from the seed rule. Finally, in the third step, \tname{} uses a 
set of heuristics to rank plausible rules.

@@

%\vspace{0.5ex}
\noindent\textbf{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks considered in our analysis.  Non-http attacks are listed at 
the top of the table and http attacks are listed at the bottom. Recall from
Section~\ref{sec:reverse-engineering} that (1) http attacks are
prevalent, (2) most http attacks use only content options, and (3)
most non-http attacks use field options only. % We selected
%\numNonContentAttacks\ non-http attacks and \numContentAttacks\ http
%attacks. The higher number of http attacks reflects their popularity.
``Name'' is the name of the attack,
``Source'' is the source where we obtained data to reproduce the
attack (see Section~\ref{subsec:malicious-traffic}), ``Type''
is the kind of attack, ``Protocol'' is the
protocol explored in the attack, and ``Ground Truth'' is the
rule options to capture the attack. The rationale for the selection
were (1) to cover various kinds of attacks and (2) to cover attacks of
various protocols. Considering (1), the selection includes attacks of
the following types: Denial-of-Service (DoS)~\cite{denial-of-service},
Active Reconnaissance (AREC)~\cite{active-reconnaissance}, Privilege
escalation (PESC)~\cite{privilege-escalation}, Remote Code Execution
(RCE)~\cite{remote-code-execution}, Local File Inclusion
(LFI)~\cite{local-file-inclusion} and ICMP Traffic Alerts \cite{icmp-types}.

@@

\noindent\textbf{Benign traffic.}~Public data sets of benign traffic
exist and can be used to evaluate the rate of false positives of
security tools. We used two popular public sources. The bigFlows.pcap
data set is part of the TcpReplay~\cite{tcpreplay} open source
project. It includes real network traffic of a private network. We
also used data sets from the Stratosphere IPS
Project~\cite{stratosphere-normal} including, for example, the regular
traffic of a university network.

\noindent\textbf{Ground Truth.}~To objectively evaluate \tname{}'s
performance we compared the rules it generates with \emph{trusted
  rules}. We used the ``Emerging Threats Open
Ruleset''~\cite{emerging-threats-open} for that. After finding a
matching pair of attack and corresponding rule using the procedure
described in Section~\ref{subsec:malicious-traffic}, we reproduced the
attack to confirm the rule captures the attack in isolation. Column
``Ground Truth'' from Table~\ref{table:attacks} only shows the
essential options. Documentation options (\eg{}, ``msg'') are
discarded.

@@

%\Mar{mention something on ethical hacking.. ethical-hacking}

This section elaborates on the most similar work to ours.

%We discuss in the following techniques similar in goal to
%ours. Unfortunately

%% As detailed before,
%% we could not access the tools implementing the techniques for
%% comparison. Nevertheless, we found that t

>>>>

To sum up, \tname{} uses the messages that manifest an attack in the
first step to create a potentially over-specified seed rule. Then, it
uses benign traffic in the second step to create a set of plausible
rules from the seed rule. Finally, in the third step, \tname{} ranks the 
plausible rules.

@@

%\vspace{0.5ex}
\noindent\textbf{Attacks.}~Table~\ref{table:attacks} outlines the
attacks considered in our analysis, where non-http attacks are at 
the top and http attacks are at the bottom. Recall from
Section~\ref{sec:reverse-engineering} that (1) http attacks are
prevalent, (2) most http attacks use content options only, and (3)
most non-http attacks use field options only. 
``Name'' is the name of the attack,
``Source'' is the source of the data to reproduce the
attack (see Section~\ref{subsec:malicious-traffic}), ``Type''
is the kind of attack, ``Protocol'' is the
protocol explored in the attack, and ``Ground Truth'' is the
rule options to capture the attack. The rationale for the selection
are attack and protocol diversity. Considering (1), 
the selection includes attacks of
the following types: Denial-of-Service (DoS)~\cite{denial-of-service},
Active Reconnaissance (AREC)~\cite{active-reconnaissance}, Privilege
escalation (PESC)~\cite{privilege-escalation}, Remote Code Execution
(RCE)~\cite{remote-code-execution}, Local File Inclusion
(LFI)~\cite{local-file-inclusion} and ICMP Traffic Alerts \cite{icmp-types}.

@@

\noindent\textbf{Benign traffic.}~Public data sets of benign traffic
exist and can be used to evaluate the rate of false positives of
security tools. We used two popular public sources. The bigFlows.pcap
data set is part of the TcpReplay~\cite{tcpreplay} open source
project. It includes real network traffic of a private network. We
also used data sets from the Stratosphere IPS
Project~\cite{stratosphere-normal} including, e.g., the regular
traffic of a university network.

\noindent\textbf{Ground Truth.}~To objectively evaluate \tname{}'s
performance, we compared the rules it generates with \emph{trusted
  rules} using the ``Emerging Threats Open
Ruleset''~\cite{emerging-threats-open}. After finding a
matching pair of attack and corresponding rule as
described in Section~\ref{subsec:malicious-traffic}, we reproduced the
attack to confirm the rule captures the attack in isolation. Column
``Ground Truth'' from Table~\ref{table:attacks} only shows the
essential options. Documentation options (\eg{}, ``msg'') are
discarded.

@@
